Learning with Mixtures of Trees

### 2022-05-23 paper/jmlr/sample.tex
first target journal picked

\usepackage{jmlr2e}
% extra packages for tables
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}

\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}

@@

\title{Accelerated oblique random survival forests}

@@

<<echo = FALSE, include = FALSE>>=

setwd(here::here())
source("packages.R")
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      dpi = 300)

rspec <- round_spec() |>
  round_using_magnitude(digits = c(3, 2, 1, 1),
                        breaks = c(1, 10, 100, Inf))

names(rspec) <- paste('table.glue', names(rspec), sep = '.')

options(rspec)

tar_load(names = c(bm_pred_comb, bm_vi_comb))

@

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
abstract here
\end{abstract}

@@

\section{Related work}

Several machine learning algorithms can engage with right-censored time-to-event outcomes. In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.

accelerated oblique random survival forests \texttt{aorsf}

original oblique random survival forests \texttt{obliqueRSF}

axis-based random survival forests \texttt{randomForestSRC \& ranger}

axis-based conditional inference forests \texttt{party}

gradient boosted decision trees \texttt{xgboost}

\section{Results}

<<>>=

results_overall <- bm_pred_comb |>
  group_by(model) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |>
  mutate(data = 'Overall')

data_tbl <- bm_pred_comb |>
  group_by(model, data, n_z, n_obs, correlated_x) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |>
  bind_rows(results_overall) |>
  mutate(
    data = if_else(
      is.na(n_z),
      true = data,
      false = as.character(
        glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr less then or equal to {correlated_x}")
      )
    )
  ) |>
  group_by(data) |>
  mutate(
    across(.cols = starts_with("time"), .fns = as.numeric),
    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
  ) |>
  arrange(data, desc(cstat_mean)) |>
  transmute(
    model = recode(
      model,
      "aorsf-15" = 'aORSF(i=15)',
      "aorsf-1" = 'aORSF(i=1)',
      "ranger" = 'Ranger',
      "xgboost" = 'Xgboost',
      "cif" = "Party",
      "randomForestSRC" = "Rfsrc",
      "coxtime" = "Coxtime"
    ),
    data = recode(
      data,
      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
      'sim' = 'Simulated data'
    ),
    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
    time_fit_mean = format(round(time_fit_mean, 3), nsmall = 3),
    time_fit_ratio = table_value(time_fit_ratio),
    time_prd_mean = format(round(time_prd_mean, 3), nsmall = 3),
    time_prd_ratio = table_value(time_prd_ratio)
  )

indents <- table(data_tbl$data)

data_tbl |>
  ungroup() |>
  select(-data) |>
  kable(booktabs=TRUE,
        longtable=TRUE,
        col.names = c(' ',
                      'C-Statistic',
                      'Scaled Brier',
                      'Mean',
                      'Ratio',
                      'Mean',
                      'Ratio'),
        align = 'lcc') |>
  pack_rows(index = indents,
            italic = TRUE,
            hline_before = TRUE,
            hline_after = TRUE) |>
  kable_styling(latex_options = c("repeat_header")) |>
  add_header_above(header = c(" " = 1,
                              "Performance metric (SD)" = 2,
                              "Fit model" = 2,
                              "Predict risk" = 2)) |>
  add_header_above(header = c(" " = 3,
                              "Computing time, seconds" = 4))

@

@@

\vskip 0.2in
\bibliography{main}

>>>>

\usepackage{jmlr2e}

@@

\title{Learning with Mixtures of Trees}

@@

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
This paper describes the mixtures-of-trees model, a probabilistic
model for discrete multidimensional domains.  Mixtures-of-trees
generalize the probabilistic trees of \citet{chow:68}
in a different and complementary direction to that of Bayesian networks.
We present efficient algorithms for learning mixtures-of-trees
models in maximum likelihood and Bayesian frameworks.
We also discuss additional efficiencies that can be
obtained when data are ``sparse,'' and we present data
structures and algorithms that exploit such sparseness.
Experimental results demonstrate the performance of the
model for both density estimation and classification.
We also discuss the sense in which tree-based classifiers
perform an implicit form of feature selection, and demonstrate
a resulting insensitivity to irrelevant attributes.
\end{abstract}

@@

Probabilistic inference has become a core technology in AI,
largely due to developments in graph-theoretic methods for the
representation and manipulation of complex probability
distributions~\citep{pearl:88}.  Whether in their guise as
directed graphs (Bayesian networks) or as undirected graphs (Markov
random fields), \emph{probabilistic graphical models} have a number
of virtues as representations of uncertainty and as inference engines.
Graphical models allow a separation between qualitative, structural
aspects of uncertain knowledge and the quantitative, parametric aspects
of uncertainty...\\

@@

\vskip 0.2in
\bibliography{sample}
